\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{helvet}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\geometry{margin=0.8in}
\setlist[itemize]{left=8pt, itemsep=0pt}
\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Esaü Bukasa}} \\
    \vspace{2pt}
    \textit{\href{mailto:esaubukasa@protonmail.com}{esaubukasa@protonmail.com} | \href{tel:+32 493 92 05 26}{+32 493 92 05 26} | \href{https://github.com/pindjouf}{https://github.com/pindjouf}}
\end{center}

\vspace{-2pt}
\hrule
\vspace{-8pt}

\section*{Professional Summary}
\vspace{-5pt}
Security professional with a background in military communications and cyber security. Experience in secure communications systems, protocol implementation, and SIEM deployment. Strong foundation in technical analysis and operational security with focus on threat detection and monitoring.

\vspace{8pt}\hrule

\section*{Work Experience}

\textbf{SOC Intern} \hfill \textit{Jan 2025 – Present} \\
Ampacimon, Loncin, Belgium
\begin{itemize}
    \item Leading deployment and configuration of ELK-based SIEM solution for enterprise security monitoring.
    \item Built internal tooling that resulted in a 19\% increase of threat actor findings.
    \item Configuring log ingestion pipelines and optimizing incident response procedures.
\end{itemize}
\vspace{8pt}

\noindent\textbf{Cybersecurity Apprenticeship} \hfill \textit{July 2024} \\
Cyber summer school, Brussels, Belgium
\begin{itemize}
    \item Admission to the bootcamp through solving different challenges linked to Cybersecurity.
    \item Lectures and workshops given by instructors from the Cyber Command: Digital Forensics, Monitoring, Malware Analysis, OSINT, ...
\end{itemize}
\vspace{8pt}

\noindent\textbf{Cybersecurity Trainee} \hfill \textit{Mar 2024 – Sep 2024} \\
BeCode, Brussels, Belgium
\begin{itemize}
    \item Developed secure code for database operations.
    \item Performed vulnerability assessments and implemented secure system configurations.
\end{itemize}
\vspace{8pt}

\noindent\textbf{ICT Operator} \hfill \textit{Apr 2023 – Feb 2024} \\
Belgian Defence, Peutie, Belgium
\begin{itemize}
    \item Managed critical communications systems and maintained strict operational security.
    \item Coordinated with multinational teams in various operations through satellite communication.
\end{itemize}

\vspace{5pt}
\hrule

\section*{Projects}
\vspace{-4pt}
\textbf{Noir Chapeau} (\textit{\href{https://noirchapeau.com}{https://noirchapeau.com}}) \hfill \textit{Launched Oct 2024}
\begin{itemize}
    \item Cybersecurity collective focused on ransomware recovery research \& data breach investigations.
\end{itemize}

\noindent\textbf{Personal Website} (\textit{\href{https://pindjouf.xyz}{https://pindjouf.xyz}}) \hfill \textit{Launched Jan 2022}
\begin{itemize}
    \item An educational resource focused on technical writing.
\end{itemize}

\vspace{5pt}

\noindent\textbf{IDY} (\textit{\href{https://idy.pindjouf.xyz}{https://idy.pindjouf.xyz}}) \hfill \textit{Launched Jan 2025}
\begin{itemize}
    \item Visualization web app for the nmap network scanner.
\end{itemize}

\vspace{5pt}\hrule

\section*{Technical Skills}
\vspace{-8pt}
\begin{itemize}
    \item \textbf{Security:} ELK Stack (SIEM), Wireshark, Burp Suite, Metasploit, Nmap, Nessus, OWASP, MITRE ATT\&CK, IDA free, Ghidra, Splunk, Malware Analysis, Pentesting, Reverse Engineering, Forensics, Linux, Active Directory
    \item \textbf{Programming \& Scripting:} Rust, Python, JavaScript/TypeScript, Bash, Verilog, C/C++, Powershell, Batch, ARM assembly, SQL
    \item \textbf{Web:} WebAssembly, React, Svelte/SvelteKit, Node.js, REST APIs, Flask, Jinja
\end{itemize}

\end{document}
